Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-09-08 paper/main.tex
paper ideasq

Description of UMM: Ekhine

new approach: add sample, learn distri, sample distri

@@

sample: peakig distri

@@

@@

We use the implementation of GECO provided by the
authors\footnote{\url{https://cran.r-project.org/package=CEGO}}. Following the
authors of CEGO~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn}, we use and
the GA that optimizes the surrogate models uses a population size of 20,
crossover rate of 0.5, mutation rate of 1, tournament selection of size 2 and
probability of 0.9, interchange mutation (i.e., exchanging two randomly
selected elements of the permutation) and cycle crossover for permutations. The
budget of each run of the GA is \textcolor{red}{$10^4$} evaluations using the
surrogate-model. Although it is never stated in the original paper, the
implementation of CEGO generates a set of initial solutions of size
$\minit=10$ by means of a max-min-distance sequential design: new solutions
are added to the set sequentially by maximizing the minimum distance to
solutions already in the set. These initial solutions are then evaluated on the
actual objective function and the result is used to build the initial surrogate
model.% \citet{ZaeStoBar2014:ppsn} uses 10

>>>>

cosas de intro : 
This new methodology relies on the assumption that the fitness landscatpe is correlated with a distribution over the same space. 
Previous paper have confirmed this point
For this case study, we show that this case for the Mallows model under the Kendall distance and

In this section, we introduce our main contribution: We present a new methodology for the optimization of black box functions with a minimal number of queries. This methodology is a probabilistic, population-based algorithm.

Essentially, the algorithm  considers a sample of permutations along with the fitness of each of them. It is an iterative process in which the number of iterations is fixed. 
Then, at each iteration, UMM (i) estimates a surrogate distribution of the fitness function and (ii) proposes a good fitted individual.

\section{Learning stage}
In this section

@@

sample: peakig distri. Borda is the

@@

prrof, probem-distri correlation

@@

We use the implementation of GECO provided by the
authors\footnote{\url{https://cran.r-project.org/package=CEGO}}. Following the
authors of CEGO~\citep{ZaeStoFriFisNauBar2014,ZaeStoBar2014:ppsn}, we use and
the GA that optimizes the surrogate models uses a population size of 20,
crossover rate of 0.5, mutation rate of 1, tournament selection of size 2 and
probability of 0.9, interchange mutation (i.e., exchanging two randomly
selected elements of the permutation) and cycle crossover for permutations. The
budget of each run of the GA is \textcolor{red}{$10^4$} evaluations using the
surrogate-model. Although it is never stated in the original paper, the	`
implementation of CEGO generates a set of initial solutions of size
$\minit=10$ by means of a max-min-distance sequential design: new solutions
are added to the set sequentially by maximizing the minimum distance to
solutions already in the set. These initial solutions are then evaluated on the
actual objective function and the result is used to build the initial surrogate
model.% \citet{ZaeStoBar2014:ppsn} uses 10
